---
title: "Developing Data Products Assignment 2"
author: "Emily Payne"
date: "10/20/2018"
output: ioslides_presentation
---

## Background

- This is the second assignment of the Developing Data Products Cousera. The purpose of this assignment is to make web page presentation that includes a plot created with the `plotly` package. 

- I decided to plot the number of vegetarian restaurants across the USA. I found the vegetarian restaurant data on the [data.world](https://data.world/datafiniti/vegetarian-vegan-restaurants) site. 

- I used the choropleth plot type to show the number of vegetarian restaurants in each state. This is indicated by the different colors of each state- the darker the blue, the more restaurants.

- You can also hover over each state to find out exactly how many vegetarian restaurants it has.
```{r, echo = FALSE, message = FALSE}
library(plotly)
library(dplyr)
library(tidyr)
vegetarianData <- read.csv("vegetarianrestaurants.csv", na.strings=c("", "NA"))
df <- data.frame(province = vegetarianData$province)
vegData <- aggregate(x = df, by = list(state = df$province), FUN = length)
names(vegData) <- c("state", "count")
vegData <- vegData[-c(4),]
vegData$state <- as.character(vegData$state)
vegData$hover <- with(vegData, paste(state, '<br>', "Number of Restaurants:", count))
borders <- list(color = toRGB("grey"), width = 0.5)
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)
```


## Plot of Vegetarian Restaurants


```{r, echo = FALSE, message = FALSE}
plot_ly(z = ~vegData$count, text = ~vegData$hover, locations = ~vegData$state, 
        type = 'choropleth', locationmode = 'USA-states', 
        color = vegData$count, colors = 'Blues', marker = list(line = borders)) %>%
  layout(title = 'Vegetarian Restaurants Across the USA', geo = map_options)
```

